decompr: GVC decomposition in R

### 2015-01-29 draft.Rnw
line breaks mostly

\section{Leontief decomposition}
\label{sec:leontief}
Let us now turn to the actual algorithms starting with the \textbf{Leontief} decomposition. We shortly describe the theoretical
derivation of the method to expose the inner steps of the \textbf{decompr} package. Then we turn to the technical implementation
and finish with a description of the output.

\subsection{Theoretical derivation}
The tools to derive the source decomposition date back to \citet{wale36} who showed that, with a set of simple calculations, 
national Input-Output tables based on gross terms give the true value added flows between industries. 
The idea behind this insight is that the production of industry \textbf{i}'s output requires inputs of other industries 
and \textbf{i}'s own value added. The latter is the direct contribution of \textbf{i}'s output to domestic value added. 
The former refers to the first round of \textbf{i}'s indirect contribution to domestic value added since the input from 
other industries that \textbf{i} requires for its own production triggers the creation of value added in the supplying 
industries. As the supplying industries usually depend on inputs from other industries, this sets in motion a second round 
of indirect value added creation in the supplying industries of the suppliers, which is also caused by \textbf{i}'s production. 
This goes on until value added is traced back to the original suppliers and can mathematically be expressed as

>>>>

\section{Leontief decomposition}
\label{sec:leontief}
Let us now turn to the algorithms, starting with the \textbf{Leontief} decomposition. We shortly describe the theoretical
derivation of the method to expose the internal steps of the \textbf{decompr} package. After which, we turn to the technical implementation.
Finally, we describe the output.

\subsection{Theoretical derivation}
The tools to derive the source decomposition date back to \citet{wale36} who showed that, with a set of simple calculations, 
national Input-Output tables based on gross terms give the true value added flows between industries. 
The idea behind this insight is that the production of industry \textbf{i}'s output requires inputs of other industries 
and \textbf{i}'s own value added.
The latter is the direct contribution of \textbf{i}'s output to domestic value added. 
The former refers to the first round of \textbf{i}'s indirect contribution to domestic value added since the input from 
other industries that \textbf{i} requires for its own production triggers the creation of value added in the supplying 
industries.
As supplying industries usually depend on inputs from other industries, this sets in motion a second round 
of indirect value added creation in the supplying industries of the suppliers, which is also caused by \textbf{i}'s production. 
This goes on until value added is traced back to the original suppliers and can mathematically be expressed as
